% This document utilises the "moderncv" package for LaTeX
% http://www.ctan.org/pkg/moderncv

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[red]{banking}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\recomputelengths

% Prevent page breaks within sections/paragraphs
\widowpenalties 1 10000
\raggedbottom

\usepackage{tabularx}
\usepackage{multicol}

% Underline some links
\usepackage[normalem]{ulem}
\newcommand\styledhref[2]{\uline{\href{#1}{#2}}}
\newcommand\styledurl[1]{\uline{\url{#1}}}

\title{Software Engineer}
\firstname{Ben}
\familyname{Brooks}
\address{1 Flixton Drive, Crewe, Cheshire}{CW2 8AP}
\phone{+44 (0)7784-144-093}
\email{ben@bbrks.me}
\homepage{bbrks.me}
%\social[linkedin]{bbrks}
\social[github]{bbrks}
%\social[twitter]{bbrks\_}

\begin{document}
	\maketitle

	\vspace{-3.5em}

	\section{Profile}
		\cvline{}{A software engineer specialised in Go, with experience of working in distributed systems, and rapid prototyping.
		Proficient in Linux-based environments, DevOps, CI/CD pipelines, automated test suites, deployments, and release management.
		}

	\section{Employment}
		\cventry
			{December 2017 - Present}{Software Engineer - Go}
			{Couchbase}{Manchester, UK/Remote}{}{
				\vspace{.25em}
					\begin{itemize}
					\item Mostly working on the open-source \styledhref{https://github.com/couchbase/sync_gateway}{Sync Gateway} project.
					\end{itemize}
				\vspace{.1em}
				\cvline{Tech}{Go, Couchbase (NoSQL), N1QL, Python, Javascript, Jenkins}
				\vspace{.25em}
			}
		\cventry
			{February 2017 - December 2017}{Software Engineer}
			{JPMorgan Chase \& Co.}{Bournemouth, Dorset, UK}{}{
				\vspace{.25em}
				\begin{itemize}
					\item \styledhref{https://github.com/jpmorganchase/quorum}{Quorum Blockchain} - Distributed Ledger and smart contract proof-of-concepts.
					\item Virtual Account Management - Prototyping and greenfield development.
				\end{itemize}
				\cvline{Tech}{Java, Javascript, Quorum/Ethereum Blockchain, Kafka, Oracle DB, Jenkins, Go}
				\vspace{.25em}
			}
		\cventry
			{June 2015 - February 2017}{Software Engineer - Go, DevOps, and Scrum Master}
			{de Poel}{Knutsford, Cheshire, UK}
			{}{
				\vspace{.25em}
				\cvline{}{Large scale rewrite of legacy invoicing/timesheet system into horizontally-scalable microservices.}
				\vspace{.1em}
				\begin{itemize}
					\item Designed and developed scalable and RESTful microservices, along with shared packages, libraries and utilities, and a high-throughput API Gateway to serve our product to the Angular, iOS, and Android apps.
					\item Shared ownership of system architecture, infrastructure, continuous integration, testing, deployment.
					\item Wrote ETLs to extract noisy data from legacy systems, sanitise, transform it, and load into new systems.
				\end{itemize}
				\cvline{Tech}{Go, Python, Javascript, MySQL, Docker, AWS, Terraform, Prometheus/Grafana, Kibana (ELK), Jenkins}
			}
			% Join above and below under same company heading.
			\vspace{-1em}
		\cventry
			{June 2015 - October 2015}{PHP Developer}
			{}{}{}{
				\begin{itemize}
					\item Developed, maintained, and supported legacy software in an agile team for client-facing products.
					\item Gained experience of working in a team using Scrum, formal code-review, and testing processes.
				\end{itemize}
				\cvline{Tech}{PHP, HTML, CSS, Javascript, MySQL}
				\vspace{.25em}
			}
		\cventry
			{February 2015 - June 2015}{WordPress Developer}
			{Webdapper}{Remote}
			{}{
				\begin{itemize}
					\item Created bespoke WordPress themes and plugins for clients.
					\item Gained remote working skills by utilising JIRA and GitHub.
				\end{itemize}
				\cvline{Tech}{PHP, HTML, CSS, Javascript, MySQL}
				\vspace{.25em}
			}
		\cventry
			{July 2013 - July 2014}{Web Developer (Industrial Year)}
			{Lighthouse Design for Business}{Shrewsbury, Shropshire, UK}{}{
				\begin{itemize}
					\item Created WordPress and Magento themes, plugins, interactive web applications with AngularJS, and static websites based on existing designs and specifications.
					\item Wrote an internal project-management app with Bootstrap and AngularJS. Backed by a PHP REST API.
				\end{itemize}
				\cvline{Tech}{PHP, HTML, CSS, Javascript, MySQL}
			}
%		\cventry
%			{June 2011 - September 2011}{1$^{st}$, 2$^{nd}$ and 3$^{rd}$ line IT support}
%			{Siemens}{Congleton, Cheshire}
%			{}{\begin{itemize}
%				\item Provided phone and in-person IT support for software, hardware and network related problems.
%				\item Maintained the factory and office networks, including VOIP phones and assembly line equipment.
%				\item Responsible for taking daily, weekly, and monthly backups and moving them off-site.
%				\item Working with one of the largest Active Directories in world (Siemens AG) to manage users and roles globally.
%			\end{itemize}}
%		\cventry
%			{June 2010 - September 2010}{Electronics Rework and Repair}
%			{Siemens}{Congleton, Cheshire}
%			{}{\begin{itemize}
%				\item Identify and replace faulty electrical components on manufactured PCBs.
%				\item Gained through hole and surface mount component soldering skills.
%			\end{itemize}}

	\section{Personal Projects}
		\cventry
			{}{Open-source projects and contributions.}
			{\href{https://github.com/bbrks}{github.com/bbrks}}{\styledurl{https://github.com/bbrks}}
			{}{\begin{itemize}
				\item \textbf{Tools} -
					\styledhref{https://github.com/bbrks/shotgun}{shotgun},
					\styledhref{https://github.com/bbrks/slow-news-day}{slow-news-day},
					\styledhref{https://github.com/bbrks/docker-dashboard}{docker-dashboard},
					\styledhref{https://github.com/bbrks/httpico}{httpico}
				\item \textbf{Go packages} -
					\styledhref{https://github.com/bbrks/wrap}{wrap},
					\styledhref{https://github.com/bbrks/chroma}{chroma},
					\styledhref{https://github.com/bbrks/midata}{midata}
			\end{itemize}}
%		\vspace{.25em}
%		\cventry
%			{February 2017 - Present}{Owner, Developer}
%			{\href{https://weighup.space}{weigh\textsuperscript{up}}}{\styledurl{https://weighup.space}}
%			{}{Web-based service. Data-driven, analytical decision-making aid. \\
%			\cvline{Tech}{Go, PostgreSQL, Docker}}
			
%		\cventry
%			{October 2016 - Present}{Owner, Developer, SysAdmin}
%			{\styledhref{https://operat.io}{Operatio}}{\styledurl{https://operat.io}}
%			{}{A simple but configurable, open-source, self-hosted task-board, written in Go and React.}
%		\cventry
%			{July 2014 - Present}{Owner, Developer, SysAdmin, Writer, Photographer}
%			{\href{https://wanderings.in}{Wanderings In...}}{\styledurl{https://wanderings.in}}
%			{}{A travel blog, featuring photography and posts from my travels.}
%		\cventry
%			{January 2010 - September 2016}{Owner, SysAdmin}
%			{TF2Dingalings}{}
%			{}{Popular community-driven site built around user-uploaded sound files for the Team Fortress 2 game.}
%		\cventry
%			{August 2007 - January 2012}{Owner, Community Manager, SysAdmin}
%			{Gluttony}{}
%			{}{Online gaming community (\textasciitilde150 members)\newline{}
%			Organised and run events, forums, several game servers, web servers, and related side-projects.}

	\section{Education}
		\cventry
			{September 2011 - June 2015}{BSc (Hons) Computer Science (BCS Accredited)}
			{University of Wales, Aberystwyth}{Aberystwyth, Ceredigion}
			{}{Second-class honours, upper division (2:1)\\Merit award scholarship in Computer Science and ICT}
				\vspace{.25em}
				\cvline{Dissertation (\styledhref{https://github.com/bbrks/AWESOME}{AWESOME})}{Web app to gather and evaluate the feedback of students for university modules. Admin dashboard creates surveys from data via university systems. Students receive tailored questionnaires and answer anonymously. Staff view results via reporting dashboards.}
				\vspace{.25em}
				\cvline{Module Results}{\vspace{-1em}
					\begin{multicols}{2}
						\begin{itemize}
							\item 1$^{st}$ - Web Development (HTML/CSS/JS)
							\item 1$^{st}$ - Web Programming (PHP/Perl)
							\item 1$^{st}$ - Interactive Web Programming (Canvas)
							\item 1$^{st}$ - System And Network Administration
							\item 1$^{st}$ - Software Development (Java)
							\item 1$^{st}$ - Advanced Computer Graphics (WebGL)
							\item 1$^{st}$ - Hardware, Operating Systems And Unix
%							\item 1$^{st}$ - Space Robotics
%							\item 1$^{st}$ - Communications And Telematics
							\item 1$^{st}$ - Professional And Personal Development
							\item 1$^{st}$ - Computer-Science Mathematics
							\item 2:1 - Internet-Based Applications (Ruby)
							\item 2:1 - Modelling Persistent Data (PostgreSQL)
							\item 2:1 - C And Unix Programming
%							\item 2:1 - Astronomy
						\end{itemize}
					\end{multicols}}

	\section{Skills}
			\vspace{-1em}
		\subsection{Languages}
			\vspace{-1em}
			\cvline{}{\begin{multicols}{4}
			\begin{itemize}
				\item Go (golang)
				\item Python
				\item JavaScript/ES6
				\item Bash/Shell
				\item Swift
				\item Java
				\item PHP
				\item C/C++
				\item Ruby (Rails)
				\item HTML
				\item CSS and SASS
				\item \LaTeX
			\end{itemize}
			\end{multicols}}
			\vspace{-1em}
		\subsection{Tools/Services}
			\vspace{-1em}
			\cvline{}{\begin{multicols}{4}
			\begin{itemize}
				\item Linux/Unix
				\item Docker/Swarm
				\item CoreOS
				\item Kubernetes
				\item Git
				\item AWS
				\item Jenkins/Hudson
				\item GitLab
				\item Terraform
				\item Kafka
				\item Elasticsearch
				\item Logstash
				\item Kibana
				\item Prometheus
				\item New Relic
				\item SonarQube
			\end{itemize}
			\end{multicols}}

	\section{Interests}
		\cvline{}{I'm usually tinkering with software, hardware, or a mixture of the two.
		But when tech gets overwhelming, I switch off by cycling, or cooking.
		Photography and travelling are also two of my passions. I combine the two, and attempt to write in a travel blog at \styledurl{https://wanderings.in}}

	\section{Contact}
		\vspace{-1em}
		\begin{multicols}{2}
			\cvline{Phone}{+44 (0)7784-144-093}
			\cvline{E-Mail}{\styledhref{mailto:ben@bbrks.me}{ben@bbrks.me}}
			\cvline{Website}{\styledurl{https://bbrks.me}}
			\cvline{LinkedIn}{\styledurl{https://linkedin.com/in/bbrks}}
			\cvline{GitHub}{\styledurl{https://github.com/bbrks}}
			\cvline{Twitter}{\styledurl{https://twitter.com/bbrks_}}
		\end{multicols}

	\section{References}
		\IfFileExists{./references.tex}{
			\input{./references.tex}
		}{
			References available upon request.
		}

\end{document}
